Supporting Information

### 2017-02-09 code/rmarkdown/figures.Rmd
address more comments

# fortify polygons
sim.pus.FPLY <- fortify(sim.pus)
aus.FPLY <- fortify(aus.PLY)
cs1.pus.FPLY <- fortify(cs1.pus)
cs2.grid.FPLY <- fortify(cs2.grid.PLY)
cs2.grid.sub.FPLY <- fortify(cs2.grid.sub.PLY)

@@

```{r, echo=FALSE, message=FALSE, fig.height=2, fig.width=2, fig.cap="Example of an attribute space. This environmental attribute space has dimensions relating to annual temperature ($^{\\circ}$C) and rainfall (mm). Letters denote the environmental conditions associated with the geographic locations where four hypothetical populations are found. Points represent demand points. In this space, populations closer to each other have similar environmental conditions."}
## generate data
# population data
populations <- data.frame(
	population=LETTERS[1:4],
	temperature=c(35,34,31,21.6),
	rainfall=c(4.5,5,9.5,5.5)   
)

@@

```{r, echo=FALSE, fig.height=1.6, fig.width=column.width, fig.cap='Distribution of environmental variation across Queensland, Australia. Squares denote planning units. Panels show the two main gradients of climatic variation.'}
# prepare data
cs1.pca.FPTS <- ldply(
	seq_len(cs1.params.LST[[MODE]]$n.pc.layers),
	function(i) {
		curr.DF <- cs1.bioclim.RAST[[i]] %>% 
			aggregate(10) %>% 
			rasterToPoints() %>% 
			as.data.frame()
		names(curr.DF)[3] <- 'Score'
		curr.DF$pc <- paste0('PC ',i)
		return(curr.DF)
	}
)
# make plots
p1 <- ggplot() +
	geom_polygon(data=aus.FPLY, aes(x=long, y=lat, group=group), fill='grey85', color='grey70') +
	geom_raster(data=filter(cs1.pca.FPTS, pc==unique(pc)[1]), aes(x=x, y=y, fill=Score)) +
	geom_polygon(data=cs1.pus.FPLY, aes(x=long, y=lat, group=group), fill=NA, color='black') +
	theme_classic() +
	theme(axis.ticks=element_blank(), axis.text=element_blank(), axis.line=element_blank(), plot.margin = unit(c(0, 0, 0, 0), "lines"),
		strip.background = element_rect(fill='grey20'),
		strip.text = element_text(color='white'),
		axis.title=element_blank(), legend.background=element_rect(color='transparent', fill='transparent'),
		legend.position=c(1.1, 1.07), legend.justification=c(1,1), legend.key.height=unit(1.5, 'mm'), legend.key.width=unit(2, 'mm')
	) +
	coord_cartesian(xlim=cs1.pus@bbox[1,], ylim=cs1.pus@bbox[2,]) +
	scale_fill_continuous(breaks=pretty(filter(cs1.pca.FPTS, pc==unique(pc)[1])$Score, n=3, min.n=2)) +
	facet_wrap(~ pc)
p2 <- ggplot() +
	geom_polygon(data=aus.FPLY, aes(x=long, y=lat, group=group), fill='grey85', color='grey70') +
	geom_raster(data=filter(cs1.pca.FPTS, pc==unique(pc)[2]), aes(x=x, y=y, fill=Score)) +
	geom_polygon(data=cs1.pus.FPLY, aes(x=long, y=lat, group=group), fill=NA, color='black') +
	theme_classic() +
	theme(axis.ticks=element_blank(), axis.text=element_blank(), axis.line=element_blank(), plot.margin = unit(c(0, 0, 0, 0), "lines"),
		strip.background = element_rect(fill='grey20'),
		strip.text = element_text(color='white'),
		axis.title=element_blank(), legend.background=element_rect(color='transparent', fill='transparent'),
		legend.position=c(1.1, 1.07), legend.justification=c(1,1), legend.key.height=unit(1.5, 'mm'), legend.key.width=unit(2, 'mm')
		) +
	coord_cartesian(xlim=cs1.pus@bbox[1,], ylim=cs1.pus@bbox[2,]) +
	scale_fill_continuous(breaks=pretty(filter(cs1.pca.FPTS, pc==unique(pc)[2])$Score, n=2, min.n=2)) +
	facet_wrap(~ pc)
# render plots
grid.arrange(p1, p2, ncol=2)
```

```{r, echo=FALSE, fig.height=2.35, fig.width=column.width, fig.cap='Distribution of the species used in the first case study. Each panel shows a different species. Squares denote planning units. Planning units occupied by a species are shown in bright blue.'}
# prepare data
cs1.pus.occ.FPLY <- ldply(
	seq_along(cs1.params.LST[[MODE]]$common.names),
	function(i) {
		curr.DF <- cs1.pus.FPLY
		curr.DF$species <- cs1.params.LST[[MODE]]$common.names[i]
		curr.DF$Occupancy <- 'absent'
		curr.DF$Occupancy[which(curr.DF$id %in% filter(cs1.ru@data@pu.species.probabilities, species==i)$pu)] <- 'present'
		return(curr.DF)
	}
)
cs1.pus.occ.FPLY$species <- factor(as.character(cs1.pus.occ.FPLY$species), levels=cs1.params.LST[[MODE]]$common.names)
# make letter data.frame
cs1.pus.occ.letters.DF <- data.frame(
	x=unname(cs1.pus@bbox[1,1] + (diff(cs1.pus@bbox[1,])*0.06)),
	y=unname(cs1.pus@bbox[2,1] + (diff(cs1.pus@bbox[2,])*0.90)),
	species=unique(cs1.pus.occ.FPLY$species),
	letter=paste0('(', letters[seq_along(unique(cs1.pus.occ.FPLY$species))], ')')
)
# make plots
ggplot() +
	geom_polygon(data=aus.FPLY, aes(x=long, y=lat, group=group), fill='grey85', color='grey70') +
	geom_polygon(data=cs1.pus.occ.FPLY, aes(x=long, y=lat, group=group, fill=Occupancy), color='black', size=0.05) +
	geom_label(data=cs1.pus.occ.letters.DF, aes(label=letter, x=x, y=y), color='black', fill=alpha('white', 0.8), size=3) +
	theme_classic() +
	theme(axis.ticks=element_blank(), axis.text=element_blank(), axis.line=element_blank(), plot.margin = unit(c(0, 0, 0, 0), "lines"),
		strip.background = element_rect(fill='grey20'),
		strip.text = element_text(color='white', size=8),
		axis.title=element_blank(), legend.position='none'
	) +
	scale_fill_manual(name='Occupancy', values=c('absent'='#132B43', 'present'='#56B1F7')) +
	coord_cartesian(xlim=cs1.pus@bbox[1,], ylim=cs1.pus@bbox[2,]) +
	facet_wrap(~ species, ncol=2)
```

```{r, echo=FALSE, fig.height=1.175, fig.width=column.width, fig.cap=paste0('Prioritizations for the first case study. Squares represent planning units. Dark green planning units were selected for protection. Panel (a) shows the planning units selected when using ',cs1.params.LST[[MODE]]$amount.target*100,' % amount targets. Panel (b) shows the planning units selected when using ',cs1.params.LST[[MODE]]$amount.target*100,' % amount targets and ',cs1.params.LST[[MODE]]$space.target*100,' % niche targets.')}
# prepare data
cs1.pus.sel.FPLY <- ldply(
	names(cs1.prioritisations),
	function(x) {
		curr.DF <- cs1.pus.FPLY
		curr.DF$Prioritisation <- x
		curr.DF$Solution <- 'discarded'
		curr.DF$Solution[curr.DF$id %in% which(as.logical(selections(cs1.prioritisations[[x]])))] <- 'selected'
		return(curr.DF)
	}
)
cs1.pus.sel.FPLY$Prioritisation <- factor(as.character(cs1.pus.sel.FPLY$Prioritisation), levels=names(cs1.prioritisations))
# make letter data.frame
cs1.pus.sel.letters.DF <- data.frame(
	x=unname(cs1.pus@bbox[1,1] + (diff(cs1.pus@bbox[1,])*0.06)),
	y=unname(cs1.pus@bbox[2,1] + (diff(cs1.pus@bbox[2,])*0.90)),
	Prioritisation=names(cs1.prioritisations),
	letter=paste0('(', letters[1:2], ')')
)
# make plots
ggplot() +
	geom_polygon(data=aus.FPLY, aes(x=long, y=lat, group=group), fill='grey85', color='grey70') +
	geom_polygon(data=cs1.pus.sel.FPLY, aes(x=long, y=lat, group=group, fill=Solution), color='black', size=0.1) +
	geom_label(data=cs1.pus.sel.letters.DF, aes(label=letter, x=x, y=y), color='black', fill=alpha('white', 0.8), size=3) +
	theme_classic() +
	theme(axis.ticks=element_blank(), axis.text=element_blank(), axis.line=element_blank(), plot.margin = unit(c(0, 0, 0, 0), "lines"),
		strip.background = element_rect(fill='grey20'),
		strip.text = element_text(color='white', size=8),
		axis.title=element_blank(), legend.position='none'
	) +
	scale_fill_manual(name='Solution', values=c('discarded'='#f7fcfd', 'selected'='#00441b')) +
	coord_cartesian(xlim=cs1.pus@bbox[1,], ylim=cs1.pus@bbox[2,]) +
	facet_wrap(~ Prioritisation, ncol=2)
```

```{r, echo=FALSE, fig.height=2.5, fig.width=column.width, fig.cap=paste0('Data used for the second case study. Squares denote planning units. Panel (a) shows all grid cells surveyed by the IntraBioDiv project. Grid cells occupied by ',tolower(cs2.params.LST[[MODE]]$common.name),' are shown in bright blue. The subsequent panels contain only show occupied grid cells. Panel (b) shows the opportunity cost of each planning unit (estimated as the total human population density). Panels (c--d) show the spatial distribution of the ordinated genetic data. These values describe the typical genetic characteristics of individuals in each planning unit. Planning units with similar values/colors contain individuals with similar loci polymorphisms.')}
# prepare full grid data
cs2.spp.grid.FPLY <- cs2.grid.FPLY
cs2.spp.grid.FPLY$Title <- 'Occupancy'
cs2.spp.grid.FPLY$Occupancy <- 'absent'
cs2.spp.grid.FPLY$Occupancy[which(cs2.grid.PLY@data[[cs2.params.LST[[MODE]]$species.name]][as.numeric(cs2.spp.grid.FPLY$id)]==1)] <- 'present'

cs2.spp.grid.letters.DF <- data.frame(
	x=unname(cs2.grid.PLY@bbox[1,1] + (diff(cs2.grid.PLY@bbox[1,])*0.06)),
	y=unname(cs2.grid.PLY@bbox[2,1] + (diff(cs2.grid.PLY@bbox[2,])*0.90)),
	letter=('(a)')
)

@@

cs2.spp.grid.sub.letters.DF <- data.frame(
	x=unname(cs2.grid.sub.PLY@bbox[1,1] + (diff(cs2.grid.sub.PLY@bbox[1,])*0.06)),
	y=unname(cs2.grid.sub.PLY@bbox[2,1] + (diff(cs2.grid.sub.PLY@bbox[2,])*0.90)),
	letter=c('(b)','(c)','(d)')
)

@@

		legend.position=c(0.25, 0.55), legend.key.height=unit(2.5, 'mm'), legend.key.width=unit(3.25, 'mm'),

@@

cs2.sel.grid.sub.letters.DF <- data.frame(
	x=unname(cs2.grid.sub.PLY@bbox[1,1] + (diff(cs2.grid.sub.PLY@bbox[1,])*0.06)),
	y=unname(cs2.grid.sub.PLY@bbox[2,1] + (diff(cs2.grid.sub.PLY@bbox[2,])*0.90)),
	letter=c('(a)','(b)')
)

>>>>

# remove small islands from australia basemap
aus.sub.PLY <- disaggregate(aus.PLY)
aus.sub.PLY <- SpatialPolygonsDataFrame(aus.sub.PLY, data=data.frame(size=gArea(aus.sub.PLY, byid=TRUE)))
aus.sub.PLY <- aus.sub.PLY[aus.sub.PLY$size >= quantile(aus.sub.PLY$size, 0.9, names=FALSE),]

# fortify polygons
sim.pus.FPLY <- fortify(sim.pus)
aus.FPLY <- fortify(aus.sub.PLY)
cs1.pus.FPLY <- fortify(cs1.pus)
cs2.grid.FPLY <- fortify(cs2.grid.PLY)
cs2.grid.sub.FPLY <- fortify(cs2.grid.sub.PLY)

@@

```{r, echo=FALSE, message=FALSE, fig.height=2, fig.width=2, fig.cap="Example of an attribute space. This environmental attribute space has dimensions relating to annual temperature ($^{\\circ}$C) and rainfall (mm). Letters denote the environmental conditions associated with the geographic locations where four hypothetical populations are found. Points represent demand points. In this space, populations closer to each other have similar environmental conditions."}
## generate data
# population data
populations <- data.frame(
	population=LETTERS[1:4],
	temperature=c(35,34,31,21.6),
	rainfall=c(4.5,5.3,9.5,5.5)   
)

@@

```{r, echo=FALSE, fig.height=1.9, fig.width=column.width, fig.cap='Distribution of environmental variation across Queensland, Australia. Squares denote planning units. Panels show the two main gradients of climatic variation.'}
# prepare data
cs1.pca.FPTS <- ldply(
	seq_len(cs1.params.LST[[MODE]]$n.pc.layers),
	function(i) {
		curr.DF <- cs1.bioclim.RAST[[i]] %>% 
			aggregate(10) %>% 
			rasterToPoints() %>% 
			as.data.frame()
		names(curr.DF)[3] <- 'Score'
		curr.DF$pc <- paste0('PC ',i)
		return(curr.DF)
	}
)
# make plots
p1 <- ggplot() +
	geom_polygon(data=aus.FPLY, aes(x=long, y=lat, group=group), fill='grey85', color='grey70') +
	geom_raster(data=filter(cs1.pca.FPTS, pc==unique(pc)[1]), aes(x=x, y=y, fill=Score)) +
	geom_polygon(data=cs1.pus.FPLY, aes(x=long, y=lat, group=group), fill=NA, color='black', size=0.05) +
	theme_classic() +
	theme(axis.ticks=element_blank(), axis.text=element_blank(), axis.line=element_blank(), plot.margin = unit(c(0, 0, 0, 0), "lines"),
		strip.background = element_rect(fill='grey20'),
		strip.text = element_text(color='white'),
		axis.title=element_blank(), legend.background=element_rect(color='transparent', fill='transparent'),
		legend.position=c(1.1, 1.07), legend.justification=c(1,1), legend.key.height=unit(1.5, 'mm'), legend.key.width=unit(2, 'mm')
	) +
  coord_cartesian(xlim=buffered.range(cs1.pus@bbox[1,], 0.025), ylim=buffered.range(cs1.pus@bbox[2,], 0.025), expand=FALSE) +
  scale_fill_continuous(breaks=pretty(filter(cs1.pca.FPTS, pc==unique(pc)[1])$Score, n=3, min.n=2)) +
	facet_wrap(~ pc)
p2 <- ggplot() +
	geom_polygon(data=aus.FPLY, aes(x=long, y=lat, group=group), fill='grey85', color='grey70') +
	geom_raster(data=filter(cs1.pca.FPTS, pc==unique(pc)[2]), aes(x=x, y=y, fill=Score)) +
	geom_polygon(data=cs1.pus.FPLY, aes(x=long, y=lat, group=group), fill=NA, color='black', size=0.05) +
	theme_classic() +
	theme(axis.ticks=element_blank(), axis.text=element_blank(), axis.line=element_blank(), plot.margin = unit(c(0, 0, 0, 0), "lines"),
		strip.background = element_rect(fill='grey20'),
		strip.text = element_text(color='white'),
		axis.title=element_blank(), legend.background=element_rect(color='transparent', fill='transparent'),
		legend.position=c(1.1, 1.07), legend.justification=c(1,1), legend.key.height=unit(1.5, 'mm'), legend.key.width=unit(2, 'mm')
		) +
  coord_cartesian(xlim=buffered.range(cs1.pus@bbox[1,], 0.025), ylim=buffered.range(cs1.pus@bbox[2,], 0.025), expand=FALSE) +
	scale_fill_continuous(breaks=pretty(filter(cs1.pca.FPTS, pc==unique(pc)[2])$Score, n=2, min.n=2)) +
	facet_wrap(~ pc)
# render plots
grid.arrange(p1, p2, ncol=2)
```

```{r, echo=FALSE, fig.height=3.8, fig.width=column.width, fig.cap='Distribution of the species used in the first case study. Each panel shows a different species. Squares denote planning units. Planning units occupied by a species are shown in bright blue.'}
# prepare data
cs1.pus.occ.FPLY <- ldply(
	seq_along(cs1.params.LST[[MODE]]$common.names),
	function(i) {
		curr.DF <- cs1.pus.FPLY
		curr.DF$species <- cs1.params.LST[[MODE]]$common.names[i]
		curr.DF$Occupancy <- 'absent'
		curr.DF$Occupancy[which(curr.DF$id %in% filter(cs1.ru@data@pu.species.probabilities, species==i)$pu)] <- 'present'
		return(curr.DF)
	}
)

cs1.pus.occ.FPLY$species <- factor(as.character(cs1.pus.occ.FPLY$species), levels=cs1.params.LST[[MODE]]$common.names)
# make letter data.frame
cs1.pus.occ.letters.DF <- data.frame(
	x=unname(cs1.pus@bbox[1,1] + (diff(cs1.pus@bbox[1,])*0.08)),
	y=unname(cs1.pus@bbox[2,1] + (diff(cs1.pus@bbox[2,])*0.95)),
	species=unique(cs1.pus.occ.FPLY$species),
	letter=paste0('(', letters[seq_along(unique(cs1.pus.occ.FPLY$species))], ')')
)
# make plots
ggplot() +
	geom_polygon(data=aus.FPLY, aes(x=long, y=lat, group=group), fill='grey85', color='grey70', size=0.05) +
	geom_polygon(data=cs1.pus.occ.FPLY, aes(x=long, y=lat, group=group, fill=Occupancy), color='black', size=0.05) +
	geom_label(data=cs1.pus.occ.letters.DF, aes(label=letter, x=x, y=y), color='black', fill=alpha('white', 0.8), size=3) +
	theme_classic() +
	theme(axis.ticks=element_blank(), axis.text=element_blank(), axis.line=element_blank(), plot.margin = unit(c(0, 0, 0, 0), "lines"),
		strip.background = element_rect(fill='grey20'),
		strip.text = element_text(color='white', size=7),
		axis.title=element_blank(), legend.position='none'
	) +
	scale_fill_manual(name='Occupancy', values=c('absent'='#132B43', 'present'='#56B1F7')) +
  coord_cartesian(xlim=buffered.range(cs1.pus@bbox[1,], 0.025), ylim=buffered.range(cs1.pus@bbox[2,], 0.025), expand=FALSE) +
	facet_wrap(~ species, ncol=2)
```

```{r, echo=FALSE, fig.height=1.9, fig.width=column.width, fig.cap=paste0('Prioritizations for the first case study. Squares represent planning units. Dark green planning units were selected for protection. Panel (a) shows the planning units selected when using ',cs1.params.LST[[MODE]]$amount.target*100,' % amount targets. Panel (b) shows the planning units selected when using ',cs1.params.LST[[MODE]]$amount.target*100,' % amount targets and ',cs1.params.LST[[MODE]]$space.target*100,' % niche targets.')}
# prepare data
cs1.pus.sel.FPLY <- ldply(
	names(cs1.prioritisations),
	function(x) {
		curr.DF <- cs1.pus.FPLY
		curr.DF$Prioritisation <- x
		curr.DF$Solution <- 'discarded'
		curr.DF$Solution[curr.DF$id %in% which(as.logical(selections(cs1.prioritisations[[x]])))] <- 'selected'
		return(curr.DF)
	}
)
cs1.pus.sel.FPLY$Prioritisation <- factor(as.character(cs1.pus.sel.FPLY$Prioritisation), levels=names(cs1.prioritisations))
# make letter data.frame
cs1.pus.sel.letters.DF <- data.frame(
	x=unname(cs1.pus@bbox[1,1] + (diff(cs1.pus@bbox[1,])*0.08)),
	y=unname(cs1.pus@bbox[2,1] + (diff(cs1.pus@bbox[2,])*0.95)),
	Prioritisation=names(cs1.prioritisations),
	letter=paste0('(', letters[1:2], ')')
)
# make plots
ggplot() +
	geom_polygon(data=aus.FPLY, aes(x=long, y=lat, group=group), fill='grey85', color='grey70', size=0.05) +
	geom_polygon(data=cs1.pus.sel.FPLY, aes(x=long, y=lat, group=group, fill=Solution), color='black', size=0.05) +
	geom_label(data=cs1.pus.sel.letters.DF, aes(label=letter, x=x, y=y), color='black', fill=alpha('white', 0.8), size=3) +
	theme_classic() +
	theme(axis.ticks=element_blank(), axis.text=element_blank(), axis.line=element_blank(), plot.margin = unit(c(0, 0, 0, 0), "lines"),
		strip.background = element_rect(fill='grey20'),
		strip.text = element_text(color='white', size=8),
		axis.title=element_blank(), legend.position='none'
	) +
	scale_fill_manual(name='Solution', values=c('discarded'='#f7fcfd', 'selected'='#00441b')) +
	coord_cartesian(xlim=buffered.range(cs1.pus@bbox[1,], 0.025), ylim=buffered.range(cs1.pus@bbox[2,], 0.025), expand=FALSE) +
	facet_wrap(~ Prioritisation, ncol=2)
```

```{r, echo=FALSE, fig.height=2.2, fig.width=column.width, fig.cap=paste0('Data used for the second case study. Squares denote planning units. Panel (a) shows all grid cells surveyed by the IntraBioDiv project. Grid cells occupied by ',tolower(cs2.params.LST[[MODE]]$common.name),' are shown in bright blue. The subsequent panels contain only show occupied grid cells. Panel (b) shows the opportunity cost of each planning unit (estimated as the total human population density). Panels (c--d) show the spatial distribution of the ordinated genetic data. These values describe the typical genetic characteristics of individuals in each planning unit. Planning units with similar values/colors contain individuals with similar loci polymorphisms.')}
# prepare full grid data
cs2.spp.grid.FPLY <- cs2.grid.FPLY
cs2.spp.grid.FPLY$Title <- 'Occupancy'
cs2.spp.grid.FPLY$Occupancy <- 'absent'
cs2.spp.grid.FPLY$Occupancy[which(cs2.grid.PLY@data[[cs2.params.LST[[MODE]]$species.name]][as.numeric(cs2.spp.grid.FPLY$id)]==1)] <- 'present'

cs2.spp.grid.letters.DF <- data.frame(
	x=unname(cs2.grid.PLY@bbox[1,1] + (diff(cs2.grid.PLY@bbox[1,])*0.07)),
	y=unname(cs2.grid.PLY@bbox[2,1] + (diff(cs2.grid.PLY@bbox[2,])*0.875)),
	letter=('(a)')
)

@@

cs2.spp.grid.sub.letters.DF <- data.frame(
	x=unname(cs2.grid.sub.PLY@bbox[1,1] + (diff(cs2.grid.sub.PLY@bbox[1,])*0.06)),
	y=unname(cs2.grid.sub.PLY@bbox[2,1] + (diff(cs2.grid.sub.PLY@bbox[2,])*0.89)),
	letter=c('(b)','(c)','(d)')
)

@@

		legend.position=c(0.25, 0.58), legend.key.height=unit(2.5, 'mm'), legend.key.width=unit(3.25, 'mm'), legend.text=element_text(size=6.0),

@@

cs2.sel.grid.sub.letters.DF <- data.frame(
	x=unname(cs2.grid.sub.PLY@bbox[1,1] + (diff(cs2.grid.sub.PLY@bbox[1,])*0.06)),
	y=unname(cs2.grid.sub.PLY@bbox[2,1] + (diff(cs2.grid.sub.PLY@bbox[2,])*0.9)),
	letter=c('(a)','(b)')
)

### 2017-02-09 code/rmarkdown/supporting-information.Rmd
address more comments

```{r, echo=FALSE, message=FALSE, fig.height=2, fig.width=2, fig.cap='insert caption here.'}
plot(1)
```

>>>>

```{r, echo=FALSE, message=FALSE, fig.height=2, fig.width=2, fig.cap='insert caption here.'}
# prepare data
plot.DF <- benchmark.results.DF %>%
  mutate(blm = paste0('BLM = ',blm))

# make plot
ggplot(plot.DF, aes(x=number.planning.units, y=time, color=number.features)) +
  geom_boxplot() +
  facet_grid(formulation ~ blm) +
  theme_classic() +
  xlab('Number of planning units) + ylab('Solve time (s)') +
  theme(axis.line.x=element_line(), axis.line.y=element_line())
```

### 2017-02-09 code/rmarkdown/text.Rmd
address more comments

Today, the most widely used conservation planning tools focus on biodiversity patterns [\texttt{Zonation} and \texttt{Marxan}; @r429; @r22]. Decision makers can use these tools to obtain solutions that secure a proportion of the geographic range of each biological feature (populations, species, or ecosystems) of interest by setting targets. One method to incorporate data on the ecological and evolutionary processes that sustain biological features is to conserve a representative sample of the physical attributes that underpin these processes. To achieve this, current methods typically involve partitioning each feature into sub-groups based on an attribute variable that relates to a biodiversity process of interest [@r9; @r247; @r448]. For instance, by dividing species distributions into sub-groups according to habitat discontinuities, and ensuring that each sub-group is represented in the solution, conservation planners can obtain prioritizations that promote adaptive processes [@r2]. However, using this method is challenging because biodiversity data are often continuous and multi-dimensional.

Simply partitioning features based on continuous variables and setting targets for each sub-group may not necessarily result in a solution that secures a representative sample of the continuous variable. For instance, if a feature was split into four sub-features based on a single continuous variable, and a solution captures 10 % of the geographic range of each sub-feature, how much of the original continuous variation does the solution represent? The answer is not immediately clear. If the solution sites reserves evenly along the original variable, then the solution may sample far more than 10 % of the original variation. Alternatively, if the solution sites reserves near the values used to divide the continuous values [as observed when partitioning features based on political boundaries; @r483], then it might sample much less of the original variation. Conventional reserve selection problems cannot differentiate between these solutions--they are both optimal--though the poorer solution may be favored when using additional constraints to reduce cost or fragmentation. This limitation has been known of quite some time. In fact, it dates back to some of the earliest reserve selection methods [eg. @r295].

>>>>

Today, the most widely used conservation planning tools focus on biodiversity patterns [\texttt{Zonation} and \texttt{Marxan}; @r429; @r22]. Decision makers can use these tools to obtain solutions that secure a proportion of the geographic range of each biological feature (populations, species, or ecosystems) of interest by setting targets. One method to incorporate data on the ecological and evolutionary processes that sustain biological features is to conserve a representative sample of the physical attributes that underpin these processes. To achieve this, current methods typically involve partitioning each feature into sub-groups based on an attribute variable that relates to a biodiversity process of interest [@r9; @r247; @r448]. For instance, by dividing species distributions into sub-groups according to habitat discontinuities, and ensuring that each sub-group is represented in the solution, conservation planners can obtain prioritizations that promote adaptive processes [@r2]. However, using this method is challenging because biodiversity often cannot be divided into operational groups for conservation planning without loss of information [@r489; @r490; @r218].

Simply partitioning features based on continuous variables and setting targets for each sub-group may not necessarily result in a solution that secures a representative sample of the continuous variable. For instance, if a feature was split into four sub-features based on a single continuous variable, and a solution captures 10 % of the geographic range of each sub-feature, how much of the original continuous variation does the solution represent? The answer is not immediately clear. If the solution sites reserves evenly along the original variable, then the solution may sample far more than 10 % of the original variation. Alternatively, if the solution sites reserves near the values used to divide the continuous values [as observed when partitioning features based on political boundaries; @r483], then it might sample much less of the original variation. Conventional reserve selection problems cannot differentiate between these solutions--they are both optimal--though the poorer solution may be favored when using additional constraints to reduce cost or fragmentation. This limitation has been known of quite some time [@r218]. In fact, it dates back to some of the earliest reserve selection methods [eg. @r295].
